Bird beak's elaboration and innovation

### 2021-11-05 Analysis/03.1-results.Rmd
Update 03.1-results.Rmd

```{r, fig.height = 20, fig.width = 10, echo = FALSE, eval = FALSE}
## Run the analyses between groups
super_results_between <- dispRity.covar.projections(superorder_shapespace,
                                             type = "groups",
                                             base = "phylogeny")
## Run the analyses between groups
order_results_between <- dispRity.covar.projections(order_shapespace,
                                             type = "groups",
                                             base = "phylogeny")
## Run the analyses of groups on the phylogeny
super_results_phylo <- dispRity.covar.projections(superorder_shapespace,
                                            type = "elements",
                                            base = "phylogeny",
                                            inc.base = TRUE,
                                            verbose = TRUE)
## Run the analyses of groups on the phylogeny
order_results_phylo <- dispRity.covar.projections(order_shapespace,
                                            type = "elements",
                                            base = "phylogeny",
                                            inc.base = TRUE,
                                            verbose = TRUE)
## Run the analyses groups on themselves
super_results_within <- dispRity.covar.projections(superorder_shapespace,
                                            type = "elements",
                                            verbose = TRUE)
## Run the analyses groups on themselves
order_results_within <- dispRity.covar.projections(order_shapespace,
                                            type = "elements",
                                            verbose = TRUE)
## Save all
shapespace_allbirds_lvl_superorder_order_results_list <- list(
        "super_results_between" = super_results_between,
        "order_results_between" = order_results_between,
        "super_results_phylo"   = super_results_phylo,
        "order_results_phylo"   = order_results_phylo,
        "super_results_within"  = super_results_within,
        "order_results_within"  = order_results_within)
save(shapespace_allbirds_lvl_superorder_order_results_list, file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list.rda")
```

>>>>

```{r, fig.height = 20, fig.width = 10, echo = FALSE, eval = TRUE}
## Run the analyses between groups
super_results_between <- dispRity.covar.projections(superorder_shapespace,
                                             type = "groups",
                                             base = "phylogeny")
## Run the analyses between groups
order_results_between <- dispRity.covar.projections(order_shapespace,
                                             type = "groups",
                                             base = "phylogeny")
## Run the analyses of groups on the phylogeny
super_results_phylo <- dispRity.covar.projections(superorder_shapespace,
                                            type = "elements",
                                            base = "phylogeny",
                                            inc.base = TRUE,
                                            verbose = TRUE)
## Run the analyses of groups on the phylogeny
order_results_phylo <- dispRity.covar.projections(order_shapespace,
                                            type = "elements",
                                            base = "phylogeny",
                                            inc.base = TRUE,
                                            verbose = TRUE)
## Run the analyses groups on themselves
super_results_within <- dispRity.covar.projections(superorder_shapespace,
                                            type = "elements",
                                            verbose = TRUE)
## Run the analyses groups on themselves
order_results_within <- dispRity.covar.projections(order_shapespace,
                                            type = "elements",
                                            verbose = TRUE)
## Save all
shapespace_allbirds_lvl_superorder_order_results_list <- list(
        "super_results_between" = super_results_between,
        "order_results_between" = order_results_between,
        "super_results_phylo"   = super_results_phylo,
        "order_results_phylo"   = order_results_phylo,
        "super_results_within"  = super_results_within,
        "order_results_within"  = order_results_within)
save(shapespace_allbirds_lvl_superorder_order_results_list, file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list.rda")
```
